---
title: Pre-processing Aurora
author: "Britt Kolen"
date: "2023-07-18"
output: html_document
---

# Version 1.01
# Changed QC pass/fail loop and subsequent merging to table.final to correct for mismatching in the original


#-Date, time and instrument columns- 
#Converting list of .csv files into dataframe 
```{r Converting list into dataframe using as.data.frame(), warning=TRUE}
DF.filedirectory<- as.data.frame(File.List.Aurora_All)
```


#Adding an .id column 
```{r Adding .id column using setDT(), warning=TRUE}
DF.filedirectoryid <- setDT(DF.filedirectory, keep.rownames = ".id")
```


#Changing second column name of dataframe to date
```{r Changing column name of dataframe to date using the rename() function, warning=TRUE}
DF.filedirectoryidDate <- DF.filedirectoryid %>% rename(Date = File.List.Aurora_All)
```


#Deleting excess text
```{r Deleting excess text using sub(), warning=TRUE}
DF.filedirectoryidDate$Date <- sub(".*?/Data_", "", DF.filedirectoryidDate$Date)
```


#Splitting the Instrument and Date columns 
```{r #Splitting the instrument and Date columns using sepreate and "/" as an identifier, warning=TRUE}
DF.filedirectoryidInstrument <- DF.filedirectoryidDate %>% separate(Date, c("Instrument", "Date"), "/")
```


#Deleting text referring to the directory in the Date column, detecting the .*?_20 in the directory name, and using sub() to replacing it with ''
```{r (Deleting text referring to the directory of the Date column, so only the Date and Time remains, warning=TRUE}
DF.filedirectoryidInstrument$Date <- sub(".*?_20", "20", DF.filedirectoryidInstrument$Date)
```


#Splitting the Date column in a date and time column, using the function seperate(), seperating on "_"
```{r Splittig the Date column in a Time and Date column, warning=TRUE}
DF.filedirectoryidTime_Date <- DF.filedirectoryidInstrument %>% separate(Date, c("Date", "Time"), "_")
```


#Final clean up of time column, removing ".csv", replacing it with '' using gsub()
```{r Final clean up of the Time column, warning=TRUE}
DF.filedirectoryidTime_Date$Time <- gsub('.CSV', '', DF.filedirectoryidTime_Date$Time)
```


#Converting the character() type dates into date() type data, using ymd()
```{r Converting data in Date column into date type data, warning=TRUE}
DF.filedirectoryidTime_Date$Date <- ymd(DF.filedirectoryidTime_Date$Date)
```


#Converting time in columns into data recognized as time data, using, parse_time
```{r Converting data in the Time column being recognized as time type Data, warning=TRUE}
DF.filedirectoryidTime_Date$Time<- parse_time(DF.filedirectoryidTime_Date $Time, "%H%M%S")
```







#-Part one of dataset-
#Importing items from list as tables with fread, specifying "," as a seperator and skipping the top of the file until "Gain".
```{r Importing files from list as tables with fread, warning=TRUE}
Tables.list<- lapply(File.List.Aurora_All, fread, header= TRUE, skip = "Gain", fill = TRUE, na.strings= "")
```

#Deleting section starting with laser settings from tables using filter() and cumsum(), based on present NA values. 
```{r (Part 1) Deleting section starting with Laser settings, warning=TRUE}
Tables.list.del <- lapply(Tables.list, filter, cumsum(Laser == "NA") == 0)
```


#Deleting the "Detector Settings" row present in the tables using !grepl
```{r (Part 1) Deleting detector settings row, warning=TRUE}
Tables.list.nodetec <- lapply(Tables.list.del, filter, !grepl("Detector Settings", Laser))
```

#Filtering out error where file has more that 8 columns
#Create replace dataframe
```{r (Part 1) Create replace dataframe, warning=TRUE}
Replace1<- data.frame(a = "", b = "", c = "", d = "", e = "", f = "", g = "", h = "")
```

#Rename columns in replace dataframe with names that fit the columns names of the other dataframes
```{r (Part 1) Rename columns in replace dataframe with names that fit the columns names of the other dataframes, warning=TRUE}
Replace1 <-  Replace1 %>%  rename("Laser"= "a", "Detector" = "b", "Gain" = "c", "Delta Gain" = "d", "% Gain Change" = "e", "Median" = "f", "% rCV" = "g", "Sensitivity" = "h")
```

#Replace any tables with column count > 8 with replace Table
```{r (Part 1) Replace any tables with column count > 8 with replace Table, warning=TRUE}
Tables.list.nodetec <- lapply(Tables.list.nodetec, function(i) {if(ncol(i) > 8) {i <- Replace1} else {i}})
```


#Binding all tables of list.nodetec together to one dataframe using rblindlist, setting idcol as true for adding date and time.
```{r (Part 1) Binding all tables together to one dataframe, warning=TRUE}
DF.tablesAurora <- rbindlist(Tables.list.nodetec, idcol=TRUE)
```


#Merging the .id dataframe with the generated dataframe based on the .id column, using merge.data.frame()
```{r (Part 1) Merging dataframes based on .id column, warning=TRUE}
DF.Aurora.id <- merge.data.frame(DF.tablesAurora, DF.filedirectoryidTime_Date, by.x= ".id")
```


#Converting the finished wide table for the first part of the total dataset, into a long table format using melt().
```{r (Part 1) Converting part one of table into long table format., warning=TRUE}
Table.done.Aurora <- melt(DF.Aurora.id, id.vars = c("Laser", "Detector", "Date", "Time", ".id", "Instrument"))
```





#-Part two of dataset-
#Importing the original list again as tables, skipping until "Laser delay" 
```{r (Part 2) Importing items from list as tables using fread for part 2 of the dataset, warning=TRUE}
Tablespt2.list <- lapply(File.List.Aurora_All, fread, header= TRUE, skip = "Laser Delay", fill = TRUE, sep = ",")
```


#Deleting lower part of the remaining table, using filter(), filtering on "FSC Area Scaling Factor"
```{r (Part 2) Deleting the lower part of the remaining table, warning=TRUE}
Tablespt2.del.list <- lapply(Tablespt2.list, filter, cumsum(Laser == "FSC Area Scaling Factor") == 0)
```
 
 
#Filtering out error where file has more that 4 columns
#Create replace dataframe
```{r (Part 2) Create replace dataframe, warning=TRUE}
Replace2<- data.frame(a = "", b = "", c = "", V4 = "")
```

#Rename columns in replace dataframe with names that fit the columns names of the other dataframes
```{r (Part 2) Rename columns in replace dataframe with names that fit the columns names of the other dataframes Table2, warning=TRUE}
Replace2 <-  Replace2 %>%  rename("Laser"= "a", "Laser Delay" = "b", "Area Scaling Factor" = "c")
```

#Replace any tables with column count > 4 with replace Table
```{r (Part 2) Rename columns in replace dataframe with names that fit the columns names of the other dataframes}
Tablespt2.del.list <- lapply(Tablespt2.del.list, function(i) {if(ncol(i) > 4) {i <- Replace2} else {i}})
```

#Binding datasets together using rbindlist()
```{r (Part 2) Binding datasets together, warning=TRUE}
DF.Aurora2.bind <- rbindlist(Tablespt2.del.list, idcol=TRUE, fill = TRUE)
```


#Merging the .id dataframe with the generated dataframe based on the .id column, using merge.data.frame()
```{r (Part 2) Merging dtaframes based on .id column}
DF.id.Aurora2 <- merge.data.frame(DF.Aurora2.bind, DF.filedirectoryidTime_Date, by.x= ".id")
```


#Adding a Detector column, used for later merging of the dataframe of the first part of the file with the second part of the file 
```{r (Part 2) Adding extra Detector column, warning=TRUE}
DF.id.Aurora2$Detector <- c("")
```


#Converting the dataframe into a long table format using melt()
```{r (Part 2) Converting part two of table into long table format., warning=TRUE}
Table.done2.Aurora <- melt(DF.id.Aurora2, id.vars = c("Laser", "Detector", "Date", "Time", ".id", "Instrument"))
```


#Using rbind() to bind the dataframes of part 1 and 2
```{r (Part 2) Binding the part 1 and part 2 tables together, warning=TRUE}
Table.done1and2.Aurora <- rbind(Table.done2.Aurora, Table.done.Aurora)
```





#-Part three of dataset-
#Importing items from list as tables with fread, specifying "," as a seperator and skipping the top of the file until "FSC Area Scaling Factor".
```{r (Part 3) Importing items from list as tables using fread for part 3 of the dataset}
Tablespt3.list<- lapply(File.List.Aurora_All, fread, header= FALSE, skip = "FSC Area Scaling Factor", fill = TRUE, na.strings= "", sep = ",")
```


#Deleting the windows extension section of the tables using subset() 
```{r (Part 3) Deleting the windows extenstion section of the tables, warning=TRUE}
Tables.nowindow3 <- lapply(Tablespt3.list, subset, select = -c(3,4))
```


#Filtering out error where file has more that 2 columns
#Create replace dataframe
```{r (Part 3) Create replace dataframe, warning=TRUE}
Replace3<- data.frame(V1 = "", V2 = "")
```

#Replace any tables with column count > 4 with replace Table
```{r (Part 3) Rename columns in replace dataframe with names that fit the columns names of the other dataframes, Table3, warning=TRUE}
Tables.nowindow3 <- lapply(Tables.nowindow3, function(i) {if(ncol(i) > 2) {i <- Replace3} else {i}})
```


#Binding datasets together using rbindlist()
```{r (Part 3) Binding datasets together, warning=TRUE}
DF.Aurora3.bind <- rbindlist(Tables.nowindow3, idcol= TRUE)
```


#Changing the column names using rename()
```{r (Part 3) Changing the column names of the 2nd and 3rd column to variable and value, warning=TRUE}
DF.Aurora3rename.bind<- rename(DF.Aurora3.bind, variable = 2, value = 3)
```


#Merging the .id dataframe with the generated dataframe based on the .id column, using merge.data.frame()
```{r (Part 3) Merging dtaframes based on .id column, warning=TRUE}
DF.id.Aurora3 <- merge.data.frame(DF.Aurora3rename.bind, DF.filedirectoryidTime_Date, by.x= ".id")
```


#Adding the "Laser" column
```{r (Part 3) Adding the Laser column, warning=TRUE}
DF.id.Aurora3$Laser <- c("")
```


#Adding the "Detector" column
```{r (Part 3) Adding the Detector column, warning=TRUE}
DF.id.Aurora3$Detector <- c("")

```


#Merging part 1,2 and 3 into a long table
```{r (Part 3) Binding the part 1, warning=TRUE}
TableFinal_Aurora <- rbind(Table.done1and2.Aurora, DF.id.Aurora3)
```





#-Post-processing of dataframe-
#Substituting all "_" values in the titels of columns the now merged dataframes using gsub()
```{r (Post) Substituting all "_" in the titles of columns, warning=TRUE}
TableFinal_Aurora$variable <- gsub(' ', '_', TableFinal_Aurora$variable)
```


#Removing the "%" from the column title %_rCV
```{r (Post) Removing the "%" from column names, warning=TRUE}
TableFinal_Aurora$variable <- gsub('%', 'Perc', TableFinal_Aurora$variable)
```


#Converting values to numeric data types, using the function as.numeric()
```{r Converting values to numberic data types, warning=TRUE}
TableFinal_Aurora$value <-as.numeric(TableFinal_Aurora$value)
```



#Writing the pass and fail function. Using case_when and mutate(). A pass and fail column in generated, the values in this column is eiter pass of fail depending on the limits for certain parameters  
```{r Writing the Pass and Fail function and creating the Pass and Fail column, warning=TRUE}
TableFinal_Aurora <- TableFinal_Aurora %>%
  mutate(Pass_and_Fail = case_when(
    variable == "Perc_Gain_Change" & value <= 100 ~ "Pass",
    variable == "Perc_Gain_Change" & value > 100 ~ "Fail",
    Detector == "UV3 (428)" & variable == "Perc_rCV" & value <= 6 ~ "Pass",
    Detector == "UV3 (428)" & variable == "Perc_rCV" & value > 6 ~ "Fail",
    Detector == "V3 (458)" & variable == "Perc_rCV" & value <= 6 ~ "Pass",
    Detector == "V3 (458)" & variable == "Perc_rCV" & value > 6 ~ "Fail",
    Detector == "R3 (697)" & variable == "Perc_rCV" & value <= 6 ~ "Pass",
    Detector == "R3 (697)" & variable == "Perc_rCV" & value > 6 ~ "Fail",
    Detector == "B3 (542)" & variable == "Perc_rCV" & value <= 6 ~ "Pass",
    Detector == "B3 (542)" & variable == "Perc_rCV" & value > 6 ~ "Fail",
    Detector == "YG3 (615)" & variable == "Perc_rCV" & value <= 6 ~ "Pass",
    Detector == "YG3 (615)" & variable == "Perc_rCV" & value > 6 ~ "Fail",
    Detector == "SSC" & variable == "Perc_rCV" & value <= 8 ~ "Pass",
    Detector == "SSC"& variable == "Perc_rCV" & value > 8 ~ "Fail",
    Detector == "SSC-B" & variable == "Perc_rCV" & value <= 8 ~ "Pass",
    Detector == "SSC-B"& variable == "Perc_rCV" & value > 8 ~ "Fail"
    
  )
  )
```



#Writing the pass and fail function. Using case_when and mutate(). Warning column in generated, the values in this column is eiter pass of fail depending on the limits for certain parameters
```{r Writing the Pass and Fail function and crating the Pass and Fail column, warning=TRUE}
TableFinal_Aurora <- TableFinal_Aurora %>%
mutate(Warning_Parameter = case_when(
    variable == "Area_Scaling_Factor" & value <= 0.9 ~ "Passed",
    variable == "Area_Scaling_Factor" & value > 0.9 ~ "Warning",
    variable == "Flow_Rate" & value > 10.5 & value < 19.5 ~ "Passed",
    variable == "Flow_Rate" & value < 10.5 ~ "Warning",
    variable == "Flow_Rate" & value > 19.5 ~ "Warning"
)
)
```



#Run after pass and fail,using is.na() all instances of NA are deleted.
```{r (Post) deleting all instances of NA, warning=TRUE}
TableFinal_Aurora[is.na(TableFinal_Aurora)] <- ""
```


#Testing removing empty space from the value column  from dataframe to remove V4
```{r (Post) removing empty space from the value column, warning=TRUE}
TableFinal_Aurora <- TableFinal_Aurora[TableFinal_Aurora$value != '', ]  
```


#Extra run to make sure values are numeric type, using as.numeric()
```{r (Post) Extra run to make sure values are of numeric type, warning=TRUE}
TableFinal_Aurora$value <-as.numeric(TableFinal_Aurora$value)
```


#Creating list that contains correct pass/fail requirements 
```{r (Post) Loop to fill in Pass anf Fill column, warning=TRUE}
List.id_columnsp_f <-lapply(unique(TableFinal_Aurora$.id),
       function(i) {
         Loop_Pass_Fail <-TableFinal_Aurora[TableFinal_Aurora$.id == i,]
         Loop_Pass_Fail<-Loop_Pass_Fail$Pass_and_Fail
         if(sum(str_detect(Loop_Pass_Fail, "Fail")) > 0){
           QC_result <-"Fail"
         } else {
           QC_result <-"Pass" 
         }
         
          data.frame(i,QC_result)

       }
)
```


#Convert list with pass/fail requirements to dataframe
```{r (Post) Convert list with pass/fail requirements to dataframe, warning=TRUE}
DF.id_columnsp_f <- as.data.frame(do.call(rbind, List.id_columnsp_f))
```


#Adding .id column to pass/fail requirement dataframe 
```{r (Post) renaming columns , warning=TRUE}
DF.id_columnsp_f2 <-  DF.id_columnsp_f %>% rename("Pass_and_Fail" = "QC_result")
DF.id_columnsp_f2 <-  DF.id_columnsp_f2 %>% rename(".id" = "i")
```



#Merging pass/fail requirements dataframe with TableFinal_Aurora
```{r (Post) Merging pass/fail requirements dataframe with TableFinal_Aurora, warning=TRUE}
TableFinal_Aurora <- merge.data.frame(TableFinal_Aurora ,DF.id_columnsp_f2, by.x= ".id", by.y = ".id")
```


#Removing empty column from TableFinal_Aurora
```{r (Post) Removing empty column from TableFinal_Aurora, warning=TRUE}
TableFinal_Aurora <- TableFinal_Aurora %>% select(-c(Pass_and_Fail.x))
```


#Rename column to Pass_and_Fail again in TableFinal_Aurora
```{r (Post) Rename column to Pass_and_Fail again in TableFinal_Aurora, warning=TRUE}
TableFinal_Aurora <-  TableFinal_Aurora %>% rename(Pass_and_Fail = Pass_and_Fail.y)
```


#Extra run 2 to make sure values are numeric type, using as.numeric()
```{r Extra run to make sure values are numeric type, warning=TRUE}
TableFinal_Aurora$value <-as.numeric(TableFinal_Aurora$value)
```


#Extra run 2 to make sure Date column only includes dates, using as.Date()
```{r (Post) Extra run 2 to make sure Date column only includes dates, using as.Date(), warning=TRUE}
TableFinal_Aurora$Date <-ymd(TableFinal_Aurora$Date)
```


#Sort based on letter and number behind Detector name in detector column 
```{r Sort based on letter and number behind Detector name in detector column , warning=TRUE}
TableFinal_Aurora$Detector<-as.factor(TableFinal_Aurora$Detector)
TableFinal_Aurora$Detector<-fct_relevel(TableFinal_Aurora$Detector,mixedsort(levels(TableFinal_Aurora$Detector)))
TableFinal_Aurora <-setorder(TableFinal_Aurora, Detector)

```

#Extra dataframe in wide table format to generate Excel file for application 
```{r (Post) Extra dataframe in wide table format to generate Excel file for application , warning=TRUE}
Wide_Table_Aurora<-dcast(TableFinal_Aurora,Date + Time + Instrument + Pass_and_Fail ~ variable+Laser+Detector, 
                  value.var = "value",
                  fun.aggregate = mean, na.rm=TRUE)
```

#Extra column for exporting of images
```{r (Post) Extra column for exporting of images, warning=TRUE}
TableFinal_Aurora$FWparams<-paste(TableFinal_Aurora$Instrument,TableFinal_Aurora$variable,TableFinal_Aurora$Laser,TableFinal_Aurora$Detector,sep="_")
```





#- Save TableFinal_Aurora and TableFinal_Aurora for RShiny application
#Save data
```{r Save the data, warning=TRUE}
save(TableFinal_Aurora, file = "Aurora.RData")
save(Wide_Table_Aurora, file = "Wide_table.RData")
```
