---
title: "RMarkdown Lyric preprocessing"
author: "Tamar Tak"
date: '2023-10-17'
output: html_document
---

```{r temporary chunk for testing, warnings=FALSE}
#library(FlowMonitorApp)
#rm(list = ls())
File.List.BDLyric_All<-list.files(path = "//vf-lumc-home.lumcnet.prod.intern/lumc-home$/ttak/MyDocs/R projects/FlowMonitor/Instrument performance tracking data/Lyric data", pattern = "PQC Report", recursive=TRUE, full.names = TRUE)
```

#-Extract date and instrument name from each .csv
#Read first line of whole table and extract only date cell
```{r Reading filname and date from list as tables with fread, warning=TRUE}
Tables.list.date<- lapply(File.List.BDLyric_All, fread, header= FALSE, nrows=1, fill = TRUE, na.strings= "")
Tables.list.date<-map(Tables.list.date, ~ (.x %>% select(V3)))
DF.Lyric.date <- rbindlist(Tables.list.date, idcol=TRUE)
colnames(DF.Lyric.date)<-c(".id","Date" )
DF.Lyric.date$Date <- gsub('Performed: ', '', DF.Lyric.date$Date)
DF.Lyric.date$Date<-parse_date_time(DF.Lyric.date$Date,orders=c("%m/%d/%Y %I:%M %p","%d-%m-%Y %H:%M"))

```


```{r Add instrument name to the date table}
DF.Lyric.date.instrument<-cbind(DF.Lyric.date,File.List.BDLyric_All)
colnames(DF.Lyric.date.instrument)<-c(".id","Date","Instrument")
DF.Lyric.date.instrument$Instrument <- sub(".*Data_", "", DF.Lyric.date.instrument$Instrument)
DF.Lyric.date.instrument$Instrument <- sub("/.*", "", DF.Lyric.date.instrument$Instrument)
```




#-Extract pass/fail status from each .csv
#Read first line of whole table and extract only date cell
```{r Importing files from list as tables with fread, warning=TRUE}
Tables.list.p_f<- lapply(File.List.BDLyric_All, fread, header= FALSE, skip = "SUMMARY",nrows=1, fill = TRUE, na.strings= "")
Tables.list.p_f<-map(Tables.list.p_f, ~ (.x %>% select(V2)))
DF.Lyric.p_f <- rbindlist(Tables.list.p_f, idcol=TRUE)
colnames(DF.Lyric.p_f)<-c(".id","Pass_and_Fail" )
```

########################################
#-Part one of dataset-
#Importing items from list as tables with fread, specifying "," as a seperator and skipping the top of the file until the word "Mirror" appears.
```{r (Part 1) Importing files from the filelist list as tables with fread starting at detector results, warning=TRUE}
Tables.list.Lyric<- lapply(File.List.BDLyric_All, fread, header= TRUE, skip = "Mirror", fill = TRUE, na.strings= "")

```

```{r correct column names that were not imported correctly due to them being on multiple lines in the .csv}
colnames.Lyric<-c( "LotInfo",
                   "Laser_Detector",
                   "Mirror",
                   "Filter",
                   "Position",
                   "PMTV_LW",
                   "Delta_PMTV_LW",
                   "Bright_Bead_Median_LW",
                   "Bright_Bead_Median_QC",
                   "perc_rCV",
                   "Linearity_Min_Channel",
                   "Linearity_Max_Channel",
                   "Resolution_Sensitivity",
                   "perc_Diff",
                   "Qr",
                   "Br")
Tables.list.Lyric<-lapply(Tables.list.Lyric, setNames, colnames.Lyric)
```


#Deleting section starting with laser settings from tables using filter() and cumsum(), based on present NA values. 
```{r (Part 1) Deleting sections after the relevant table by looking for an empty column, warning=TRUE}
Tables.list.Lyric.del <- lapply(Tables.list.Lyric, filter, cumsum(LotInfo == "NA") == 0)
```


#Binding all tables of list.nodetec together to one dataframe using rblindlist, setting idcol as true for adding date and time.
```{r (Part 1) Binding all tables together to one dataframe, warning=TRUE}
DF.tablesLyric <- rbindlist(Tables.list.Lyric.del, idcol=TRUE)

```

```{r (Part 1) remove LotInfo column as it doesnt contain data, warning=TRUE}
DF.tablesLyric<-select(DF.tablesLyric, -c(LotInfo,Mirror,Filter,Position))

```

# Merge the detector table with the date and QC tables 
```{r (Part 1) Merging dataframes based on .id column, warning=TRUE}
DF.Lyric.id <- merge.data.frame(DF.tablesLyric, DF.Lyric.date.instrument, by= ".id")
DF.Lyric.id <- merge.data.frame(DF.Lyric.id, DF.Lyric.p_f, by= ".id")
```

#Converting the finished wide table for the first part of the total dataset, into a long table format using melt().
```{r (Part 1) Converting part one of table into long table format., warning=TRUE}
Table.done.lyric <- reshape2::melt(DF.Lyric.id, id.vars = c("Laser_Detector" ,"Date", ".id", "Instrument","Pass_and_Fail"))
```


###############################
#-Part two of dataset-
#Importing the original list again as tables, skipping until "Trigger" 
```{r (Part 2) Importing items from list as tables using fread for part 2 of the dataset, warning=TRUE}
Tables.list.Lyric.laser<- lapply(File.List.BDLyric_All, fread, header= TRUE, skip = "Area Scaling Factor", fill = TRUE, na.strings= "")
```


```{r (Part 2) correct column names that were not imported correctly due to them being on multiple lines in the .csv}
colnames.Lyric.laser<-c( "Laser_Detector",
                         "Position",
                         "Delay_(FSC)",
                         "Delay_(Fluorescence)",
                         "Area_Scaling_Factor",
                         "Power_(mW)",
                         "Power_Spec",
                         "Current_(mA)",
                         "Current_Spec"   
                         )
Tables.list.Lyric.laser<-lapply(Tables.list.Lyric.laser, setNames, colnames.Lyric.laser)
```


#Deleting lower part of the remaining table, using filter(), filtering on "FSC Area Scaling Factor"
```{r (Part 2) Deleting the lower part of the remaining table, warning=TRUE}
Tables.list.Lyric.laser.del <- lapply(Tables.list.Lyric.laser, filter, cumsum(Laser_Detector == "INFO") == 0)
```
 
 
#convert list of dataframes into a single dataframe using rbindlist()
```{r (Part 2) Binding datasets together, warning=TRUE}
DF.Lyric2.bind <- rbindlist(Tables.list.Lyric.laser.del, idcol=TRUE, fill = TRUE)
```
 
 
#Merging the .id dataframe with the generated dataframe based on the .id column, using merge.data.frame()
```{r (Part 2) Merging dtaframes based on .id column}
DF.id.Lyric2 <- merge.data.frame(DF.Lyric2.bind, DF.Lyric.date.instrument, by= ".id")
DF.id.Lyric2 <- merge.data.frame(DF.id.Lyric2, DF.Lyric.p_f, by= ".id")
```


#Converting the dataframe into a long table format using melt()
```{r (Part 2) Converting part two of table into long table format., warning=TRUE}
Table.done2.lyric <- reshape2::melt(DF.id.Lyric2, id.vars = c("Laser_Detector" ,"Date", ".id", "Instrument","Pass_and_Fail"))
```


#Using rbind() to bind the dataframes of part 1 and 2
```{r (Part 2) Binding the part 1 and part 2 tables together, warning=TRUE}
Table.done1and2.lyric <- rbind(Table.done.lyric, Table.done2.lyric)
```






###########
#-Part three of dataset-
#Importing the original list again as tables, skipping until "Item" 
```{r (Part 3) Importing items from list as tables using fread for part 3 of the dataset, warning=TRUE}
Tablespt3.list <- lapply(File.List.BDLyric_All, fread, header= FALSE, 
                         skip = "Lot ID:", fill = TRUE, nrows=1)
```

#Binding datasets together using rbindlist()
```{r (Part 3) Binding datasets together, warning=TRUE}
DF.lyric3.bind <- rbindlist(Tablespt3.list, idcol=TRUE, fill = TRUE)
```

```{r remove unnecessary columns, rename columns and add an empty Laser_Detector column}
DF.lyric3.bind<-select(DF.lyric3.bind, -c(V1, V3))
colnames(DF.lyric3.bind)<-c(".id", "BeadLot","FSC_Area_Scaling_Factor")
DF.lyric3.bind$Laser_Detector<-""
```


#Merging the .id dataframe with the generated dataframe based on the .id column, using merge.data.frame()
```{r (Part 3) Merging dtaframes based on .id column}
DF.id.Lyric3 <- merge.data.frame(DF.lyric3.bind, DF.Lyric.date.instrument, by= ".id")
DF.id.Lyric3 <- merge.data.frame(DF.id.Lyric3, DF.Lyric.p_f, by= ".id")
```

#Converting the dataframe into a long table format using melt()
```{r (Part 3) Converting part three of table into long table format., warning=TRUE}
Table.done3.lyric <- reshape2::melt(DF.id.Lyric3, id.vars = c("Laser_Detector" ,"Date", ".id", "Instrument","Pass_and_Fail"))
```



#Using rbind() to bind the dataframes of part 1+2 and 3
```{r (Part 3) Binding the part 1 and part 2 tables together, warning=TRUE}
TableFinal_BDLyric <- rbind(Table.done1and2.lyric,Table.done3.lyric)
```



levels(as.factor(TableFinal_BDLyric$Laser_Detector))



#-Post-processing of dataframe-

#Converting values to numeric data types, using the function as.numeric()
```{r (Post) Converting values to numberic data types, warning=TRUE}
TableFinal_BDLyric$Date <-as.Date(TableFinal_BDLyric$Date)
TableFinal_BDLyric$value <-as.numeric(TableFinal_BDLyric$value)
```

#Remove NAs from value column.
```{r (Post) deleting all instances of NA, warning=TRUE}

TableFinal_BDLyric <- TableFinal_BDLyric %>%
         drop_na(value)
```



```{r (Post) reorder table alphabetically}
    TableFinal_BDLyric<-TableFinal_BDLyric %>% arrange(Instrument,variable,Laser_Detector,Date)
```

##########################
#Extra dataframe in wide table format to generate Excel file for application 
```{r (Post) Extra dataframe in wide table format to generate Excel file for application , warning=TRUE}
Wide_Table_Lyric<-reshape2::dcast(TableFinal_BDLyric,Date + Instrument + Pass_and_Fail ~ variable + Laser_Detector, 
                  value.var = "value",
                  fun.aggregate = mean, na.rm=TRUE)
```

#Extra column for exporting of images
```{r (Post) Extra column for exporting of images, warning=TRUE}
TableFinal_BDLyric$FWparams<-paste(TableFinal_BDLyric$Instrument,TableFinal_BDLyric$variable,TableFinal_BDLyric$Laser_Detector,sep="_")
```


#- Save TableFinal_BDLyric and TableFinal_BDLyric for RShiny application
#Save data
```{r Save the data, warning=TRUE}
save(TableFinal_BDLyric, file = "TableFinal_BDLyric.RData")
save(Wide_Table_Lyric, file = "Wide_Table_BDLyric.RData")
```


